%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands

\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeItemBig}[2]{\item{\textbf{#1}}}
\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}
\newcommand{\resumeSubItem}[2]{\item\small{\textbf{#1}{#2 \vspace{-0.5pt}}}}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{{\Large Divyanshu Alok}} & Email : {divyanshuncs@gmail.com}\\
& Mobile : +91-7798805229 \\
\url{www.linkedin.com/in/divyanshu-alok}& \href{https://github.com/DivyanshuAlok}{GitHub : /DivyanshuAlok} \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
 \resumeSubheading
	  {DX FutureTech}{Bengaluru, Karnataka}
	  {React Native Developer}{June 2024 - Present}
	  \resumeItemListStart
\resumeSubItem{}{Developed a B2C app for UK property management, optimizing processes for buying, renting, and selling.}
\resumeSubItem{}{Created a B2B property management solution for UAE, digitizing real estate operations.}
\resumeSubItem{}{Architected modular, high-performance applications with reusable components and future-proof, scalable architecture.}
\resumeSubItem{}{Implemented login functionality with biometric authentication and guest login for enhanced user access and convenience.}
\resumeSubItem{}{Added offline compatibility using WatermelonDB, ensuring uninterrupted app functionality in low-connectivity environments.}
\resumeSubItem{}{Built fuzzy search and sort capabilities, enabling users to filter and discover properties efficiently.}
\resumeSubItem{}{Integrated Google Maps and Directions API to provide real-time navigation and geolocation support for property listings.}
\resumeSubItem{}{Enabled in-app PDF export for generating and sharing professional reports.}
\resumeSubItem{}{Integrated GraphQL APIs and payment gateways, enabling seamless user experiences on iOS and Android.}
\resumeSubItem{}{Embedded YouTube video integration for dynamic content delivery within listings and informational sections.}
\resumeSubItem{}{Led the development of advanced features like animations, notifications, and in-app purchases.}
\resumeSubItem{}{Enhanced app security with secure credentials and role-based access control.}
\resumeSubItem{}{Integrated native modules to enhance performance and enable advanced platform-specific functionality.}
\resumeSubItem{}{Streamlined CI/CD pipelines using GitHub Actions for automated testing and deployment.}
\resumeSubItem{}{Contributed to mobile performance optimization efforts by profiling, debugging, and reducing render lag and memory consumption.}

	\resumeItemListEnd


  \resumeSubheading
	  {LTIMindtree}{Hyderabad, Telangana}
	  {Senior Software Engineer - React Native}{Oct 2020 - June 2024}
	  \resumeItemListStart
	  	\resumeSubItem{}{Led cross-platform app development, integrating chatbots, payment systems, and inventory features.}
\resumeSubItem{}{Designed app architecture with Redux Saga/Thunk and enabled offline database support using WatermelonDB.}
\resumeSubItem{}{Integrated RESTful and GraphQL APIs, ensuring robust backend communication.}
\resumeSubItem{}{Streamlined CI/CD with CircleCI and GitHub Actions, optimizing DevOps processes.}
\resumeSubItem{}{Enhanced performance with React Native Skia and Reanimated for rich graphics.}
\resumeSubItem{}{Collaborated closely with cross-functional teams and mentored junior developers during sprint planning and code reviews.}
	\resumeItemListEnd

\resumeSubheading
{Freelance Mobile Application Developer}{Hyderabad, Telangana}
{Mobile Application Developer}{June 2019 - Aug 2020}
\resumeItemListStart
\resumeItem{Feazy (Protron Technologies)}
{Built a contactless dining app with QR code scanning and integrated payments.}
\resumeItem{Technology Stack}
{React-Native, Firebase (PostGIS),QRcode-Scanner}
\resumeItem{Ridesharing App (AONE Apps)}
{Developed a cross-platform ridesharing app with real-time mapping and location tracking.}
\resumeItem{Technology Stack}
{React Native, Firebase, MapBox, Google Maps}
\resumeSubItem{}{Deployed mobile applications to both the Google Play Store and Apple App Store, ensuring production readiness and post-release support.}
\resumeItemListEnd

  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\resumeSubItem{Technologies}{ React-Native, Android, React-js, Node.js, Redux, GIT, Firebase, RPA, Power Platform, Whiteboarding.}
\resumeSubItem{Languages}{: JavaScript (4 Years), HTML, CSS, Python, SQL, Bash, Flex, ES6}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeItem{Pratibha }
{Developed an app connecting underprivileged students with mentors.}
\resumeItem{Adverse Road Condition Map}
{Map-based app for road hazard alerts, recognized as Smart India Hackathon 2019 Winner.}
\resumeSubHeadingListEnd

%--------Achievements------------
\section{Achievements}
\resumeSubHeadingListStart
  \resumeItem{1st position}
{Smart India Hackathon 2019 Winner for complex problem statement.}
\resumeItem{Spotlight award 2022}
{Received the Spotlight Award for consistently and punctually delivering critical use cases.}
  \resumeSubHeadingListEnd




%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Chaitanya Bharathi Institute Of Technology}{Hyderabad, TS}
  {Bachelor of Technology in Information Technology;}{2016 - 2020}
  \resumeSubheading
  {Navy Children School}{Port Blair, A\&N}
  {Intermediate;}{2013 - 2015}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}