%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands

\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}
\newcommand{\resumeSubItem}[2]{\item\small{\textbf{#1}{#2 \vspace{-2pt}}}}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{{\Large Divyanshu Alok}} & Email : {divyanshuncs@gmail.com}\\
& Mobile : +91-7798805229 \\
\href{www.linkedin.com/in/divyanshu-alok}{www.linkedin.com/in/divyanshu-alok}& GitHub : /DivyanshuAlok \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
	  {LTIMindtree}{Hyderabad, Talengana}
	  {Senior Software Engineer - Automation}{Oct 2020 - Present}
	  \resumeItemListStart
		  \resumeItem{Braio }{BRAIO is a Service Automation solution based on JBPM that includes Automation of Runbook and Workflow Management.}
		  \resumeItemListStart
			  \resumeItem{Automated VM Provisioning }
			  {Developed a workflow to automate VM Provisioning on Openstack platform (based on Nutanix) with Runbooks written in PowerShell and Python and utilized ServiceNow ITSM to monitor its progress, increasing time efficiency by 80\%.}
			\vspace{3pt}
			\resumeSubItem{}
			  {Developed 10+ sets of runbooks and workflows to streamline and automate activities across several domains, including Windows AD, Hyper-V, MSSQL, PSQL and OS Patching saving approximately 70\% FTE per use case.}
			  \resumeItemListEnd
		\vspace{4pt}
		\resumeItem{Power Automate }
		  {Developed a desktop based automated process with a cloud trigger to perform sanity checks with report generation on a number of client websites resulting in more than 70\% reduction in manual task.}
		\resumeItem{Power Apps }
		  {Developed an AI/ML resource management site using PowerApps and Power Automate for backend logic.}
		\resumeItem{Service Now Workflow }
		  {Developed a handful of ServiceNow workflows to automate tasks associated with various domains, and afterwards presented the capabilities of these workflows on the ServiceNow marketplace.}
	\resumeItemListEnd

  \resumeSubheading
    {Protron Technologies}{Hyderabad, Talengana}
    {Mobile Application Developer}{June 2020 - July 2020}
    \resumeItemListStart
      \resumeItem{Feazy - Contactless Dining}
      {Developed a cross-platform mobile application using React-Native with a payment gateway, allowing customers to order food from a food court within minutes and reduce waiting time considerably.}
      \resumeItem{Technology Stack}
      {React-Native, Firebase (PostGIS)}
    \resumeItemListEnd


  \resumeSubheading
    {AONE Apps}{Hyderabad, Talengana}
    {Mobile Application Developer}{June 2019 - Aug 2019}
    \resumeItemListStart
      \resumeItem{AONE : Nextgen Ridesharing}
      {Developed a comparable iOS app for an Android app already in use with  the intention to shift the technological stack from platform-native codebase  to one with a singular codebase.}
      \resumeItem{Technology Stack}
      {React-Native, Firebase, MapBox, Google Maps}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Chaitanya Bharathi Institute Of Technology}{Hyderabad, TS}
  {Bachelor of Technology in Information Technology;  GPA: 6.20}{2016 - 2020}
  \resumeSubheading
  {Navy Children School}{Port Blair, A\&N}
  {Intermediate;  Percentage : 84\%}{2013 - 2015}
  \resumeSubHeadingListEnd



%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeItem{Adverse Road Condition Map}
{Map based application to alert the user regarding potholes and speed bumps. The data is collected by the user itself.(Smart India Hackathon 2019 Problem statement, given by ARAI)}
\resumeItem{Spam detection and sentiment analysis}
{Application based on Machine Learning using python to detect spam set of texts and further perform sentiment analysis. Tested on the Twitter data set.}
\resumeItem{Parent Pal}
{Cross-platform mobile application to monitor application usage of target device (ios or android).}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
\resumeSubHeadingListEnd

%--------Achievements------------
\section{Achievements}
\resumeSubHeadingListStart
  \resumeItem{1st position}
{Smart India Hackathon 2019 Winner for complex problem statement.}

  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\resumeSubItem{Technologies}{ ServiceNow Orchestration (Workflow Automation) , Power Automate, React-Native, React-js, Power Apps, Runbook Automation.}
\resumeSubItem{Languages}{: Python, Javascript, Powershell, C++, SQL, Bash}

\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}